
\documentclass[10pt]{article}
\usepackage[a4paper,margin=14mm]{geometry}
\usepackage{xcolor}
\usepackage{fontspec}
\setmainfont{Georgia}
\setsansfont{Arial}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.35em}
\definecolor{accent}{HTML}{C92A2A}

\begin{document}

{\sffamily\footnotesize Generated 2026-03-18\par}
{\sffamily\bfseries\fontsize{24}{26}\selectfont\color{accent} Mikkel Stahlschmidt\par}
PhD student at the Department of Economics, University of Copenhagen, and the ROCKWOOL Foundation Interventions Unit.\par
University of Copenhagen and ROCKWOOL Foundation Interventions Unit\par

{\sffamily\footnotesize Website: https://econmikkel.github.io \hfill Email: mis@rfintervention.dk\par}
{\sffamily\footnotesize Google Scholar: https://scholar.google.com/citations?user=VfLh5XEAAAAJ\par}
{\sffamily\footnotesize ORCID: https://orcid.org/0009-0007-2392-6470\par}

\vspace{0.5em}
\fcolorbox{accent!15}{accent!4}{%
  \parbox{0.97\linewidth}{%
    This one-page overview is intended for non-academic visitors who want a quick sense of the themes, collaborators, and applied relevance of my work.\par
    \textbf{Main themes:} migration and integration, survey methods, and applied policy evaluation.
  }%
}

\vspace{0.9em}
{\sffamily\bfseries\color{accent} Journal articles\par}
\vspace{0.35em}
{\footnotesize No items listed yet.\par}
\vspace{0.55em}
{\sffamily\bfseries\color{accent} Working papers and projects\par}
\vspace{0.35em}
\textbf{How Initial Accommodation Shapes Refugee Integration: Quasi-Experimental Evidence from the Ukrainian Displacement Crisis in Denmark}\par
{\footnotesize Mette Foged, Jens Hainmueller, Mikkel Stahlschmidt, Edith Zink | ROCKWOOL Foundation Berlin working paper | In press}\par
Quasi-experimental evidence on how initial accommodation conditions shape refugee integration outcomes.\par
\vspace{0.6em}
\textbf{What do we gain (and lose) from responsive questions? Comparing open-ended survey questions with adaptive probes from an AI interviewer}\par
{\footnotesize Hjalmar Alexander Bang Carlsen, Tobias Priesholm Gårdhus, Mikkel Stahlschmidt | Open Science Framework | Pre-registered project}\par
A project comparing traditional open-ended survey questions with adaptive AI-assisted interviewing.\par
\vspace{0.6em}
\vspace{0.55em}
{\sffamily\bfseries\color{accent} Non-academic work\par}
\vspace{0.35em}
{\footnotesize No items listed yet.\par}
\vspace{0.55em}

\vfill
{\sffamily\footnotesize\color{black!65} Disclaimer: This PDF is generated automatically by OpenAI Codex when the website is updated. I do not guarantee that the information is correct.\par}

\end{document}
